### 2023-07-20 supporting.tex
Added diversity criteria table to supplement

>>>>

\begin{table}[h!]
\centering
\caption{\textbf{Phylogenetic diversity criteria.}}
\label{stable:diversity_criteria}
\begin{tabular}{|l|l|}
\hline
\textbf{Species IDs}   & \textbf{Minimum number}   \\ \hline
dinn,   dgri, dhyd     & 2                         \\ \hline
dnov,   dvir           & 1                         \\ \hline
dmoj,   dnav           & 1                         \\ \hline
dper,   dpse           & 1                         \\ \hline
dgua,   dsob           & 1                         \\ \hline
dana,   dbip           & 1                         \\ \hline
dkik,   dser           & 1                         \\ \hline
dele,   drho           & 1                         \\ \hline
dtak,   dbia           & 1                         \\ \hline
dspu,   dsuz           & 1                         \\ \hline
dere,   dtei           & 1                         \\ \hline
dsan,   dyak           & 1                         \\ \hline
dmel                   & 1                         \\ \hline
dmau,   dsec, dsim     & 1                         \\ \hline
\end{tabular}
\end{table}
